---
title: "IMDB Movie Finder"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: PP_logotyp_ANG_RGB.png
runtime: shiny
---


<style>
.navbar-logo img {
  max-height: 80px !important; 
  width: auto !important;
}

.navbar {
  height: 80px !important;
  min-height: 80px !important; 
}
body {
  padding-top: 80px !important; 
}

.navbar-header {
  display: flex !important;
  align-items: center !important; 
  height: 80px !important;       
  width: 100% !important;
}

.navbar-logo {
  display: flex !important;
  align-items: center !important;
  padding-left: 15px !important;
  position: static !important;
}

.navbar-brand {
  flex-grow: 1 !important;
  display: flex !important;
  justify-content: center !important;
  align-items: center !important;
  margin: 0 !important;
  padding: 0 !important;
  
  font-family: 'Segoe UI', Roboto, Helvetica, Arial, sans-serif !important;
  font-size: 26px !important; 
  font-weight: 800 !important; 
  letter-spacing: 1.5px !important;
  color: #F7F7F7 !important;  
  text-shadow: 1px 1px 2px rgba(0,0,0,0.1) !important;
}
</style>


```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(plotly)
library(shiny)
library(DT)
library(tidyr)
library(dplyr)
library(stringr)
library(readr)
library(jsonlite)
```

```{r, include=FALSE}
data = read.csv("imdb_top_1000.csv")
```

Column {data-width=250}
-----------------------------------------------------------------------

### Movie Datatable

```{r}
# Movie table logic

# This makes it reactive
DTOutput("movie_table")
output$movie_table = renderDT({
  table_data = data %>%
    select("Series_Title", "Released_Year", "Director", "IMDB_Rating")

datatable(table_data,
          selection = list(mode = 'single', selected = 1),
          class = 'display compact',
          rownames = FALSE,
          options = list(
            pageLength = 24,
            autoWidth = TRUE,
            searchHighlight = TRUE))
})
```

Column {data-width=350}
-----------------------------------------------------------------------

###

```{r}
# Poster logic
output$poster_ui = renderUI({
  req(input$movie_table_rows_selected)
  
  selected_idx = input$movie_table_rows_selected
  
  img_url = data$Poster_Link[selected_idx]
  
  tags$img(src = img_url, style = "height: 100%; width: 100%; object-fit: contain; border-radius: 8px; filter: drop-shadow(2px 2px 5px rgba(0,0,0,0.2));")
})


# Stars logic
output$rating_ui = renderUI({
  req(input$movie_table_rows_selected) 
  selected_idx = input$movie_table_rows_selected
  
  rating = as.numeric(data$IMDB_Rating[selected_idx])
  rating_text = sprintf("%.1f", rating)
  star_pct = round((rating / 10) * 100, 1)
  
  HTML(paste0('
    <div style="text-align: center; display: flex; flex-direction: column; justify-content: center; height: 100%;">
      <div style="font-size: 96px; font-weight: 900; color: #333; line-height: 1;">', rating_text, '</div>
      
      <div style="margin-top: 8px;">
        <span style="font-size: 56px; 
                     background: linear-gradient(90deg, #F4B400 ', star_pct, '%, #e0e0e0 ', star_pct, '%);
                     -webkit-background-clip: text;
                     -webkit-text-fill-color: transparent;
                     display: inline-block;">
          ★★★★★★★★★★
        </span>
      </div>
      
    </div>
  '))
})
```

<div style="display: flex; gap: 10px; height: 100%;">
  <div style="flex: 1; text-align: left; height: 100%;">
```{r}
# Poster displayed
uiOutput("poster_ui", style = "height: 100%;")
```
  </div>
  <div style="flex: 4; height: 100%; overflow-y: auto;">
```{r}
# Stars displayed
uiOutput("rating_ui", style = "height: 100%;")
```
  </div>
</div>

### Actors

```{r}
# Getting images
get_tmdb_image = function(actor_name, api_key) {
  safe_name = URLencode(trimws(actor_name))
  
  tmdb_api_url = paste0("https://", "api.themoviedb.org/3/search/person?query=", safe_name, "&api_key=", api_key)
  tmdb_img_base = paste0("https://", "image.tmdb.org/t/p/w200")
  fallback_base = paste0("https://", "[ui-avatars.com/api/?name=](https://ui-avatars.com/api/?name=)", safe_name, "&background=random&color=fff&size=150&bold=true")
  
  img_url = tryCatch({
    api_data = jsonlite::fromJSON(tmdb_api_url)
    
    if (!is.null(api_data$results) && is.data.frame(api_data$results) && nrow(api_data$results) > 0) {
      p_path = api_data$results$profile_path[1]
      
      if (!is.null(p_path) && !is.na(p_path) && p_path != "") {
        message("TMDB SUCCESS: Found photo for ", actor_name)
        return(paste0(tmdb_img_base, p_path))
      }
    }
    
    message("TMDB WARNING: ", actor_name, " found, but has no profile picture. Using fallback.")
    return(fallback_base)
    
  }, error = function(e) {
    message("TMDB CRITICAL ERROR for ", actor_name, ": ", e$message)
    return(fallback_base)
  })
  
  return(img_url)
}
```

```{r}
# Actor displaying logic
output$cast_ui = renderUI({
  req(input$movie_table_rows_selected) 
  selected_idx = input$movie_table_rows_selected

  tmdb_key = "46c2ebcda9588c28b102306512e4161a" 
  
  actors = c(
    trimws(data$Star1[selected_idx]),
    trimws(data$Star2[selected_idx]),
    trimws(data$Star3[selected_idx]),
    trimws(data$Star4[selected_idx])
  )
  
  actors = actors[!is.na(actors) & actors != ""]
  
  actor_cards = lapply(actors, function(name) {
    img_url = get_tmdb_image(name, tmdb_key)
    
    paste0('
      <div style="display: flex; flex-direction: column; align-items: center; width: 100px; margin: 10px;">
        <img src="', img_url, '" style="width: 75px; height: 75px; border-radius: 50%; object-fit: cover; box-shadow: 0 4px 6px rgba(0,0,0,0.1); border: 2px solid #eee;">
        <div style="font-size: 13px; font-weight: 600; text-align: center; margin-top: 8px; color: #444; line-height: 1.2;">', name, '</div>
      </div>
    ')
  })
  
  HTML(paste0('
    <div style="display: flex; flex-direction: row; flex-wrap: wrap; justify-content: space-evenly; align-items: flex-start; width: 100%; padding-top: 10px;">', 
      paste(actor_cards, collapse = ""), 
    '</div>
  '))
})
```

```{r}
# Actors displayed
uiOutput("cast_ui")
```

### More by Director

```{r}
# Logic for other movies by the same director
output$director_movies_ui = renderUI({
  # Ensure a row is selected
  req(input$movie_table_rows_selected) 
  
  selected_idx = input$movie_table_rows_selected
  
  # Get the current movie and director
  current_director = data$Director[selected_idx]
  current_movie = data$Series_Title[selected_idx]
  
  # Filter dataset for same director, but exclude the current movie
  other_movies = data %>%
    filter(Director == current_director & Series_Title != current_movie)
  
  # Handle cases where the director has no other movies in the top 1000
  if (nrow(other_movies) == 0) {
    return(HTML(paste0(
      '<div style="text-align: center; padding: 20px; color: #777; font-style: italic;">',
      'No other movies by ', current_director, ' in the Top 1000.',
      '</div>'
    )))
  }
  
  # Build HTML cards for each movie found
  movie_cards = lapply(1:nrow(other_movies), function(i) {
    img_url = other_movies$Poster_Link[i]
    title = other_movies$Series_Title[i]
    
    paste0('
      <div style="display: flex; flex-direction: column; align-items: center; width: 110px; flex-shrink: 0; margin-right: 15px;">
        <img src="', img_url, '" style="width: 100px; height: 140px; border-radius: 6px; object-fit: cover; box-shadow: 0 4px 6px rgba(0,0,0,0.15);">
        <div style="font-size: 12px; font-weight: 600; text-align: center; margin-top: 8px; color: #333; line-height: 1.2;">', title, '</div>
      </div>
    ')
  })
  
  # Wrap the cards in a horizontally scrolling flex container
  HTML(paste0('
    <div style="font-weight: 600; font-size: 16px; margin-bottom: 10px; color: #444;">
      More by ', current_director, '
    </div>
    <div style="display: flex; flex-direction: row; flex-wrap: nowrap; overflow-x: auto; padding-bottom: 10px; width: 100%;">', 
      paste(movie_cards, collapse = ""), 
    '</div>
  '))
})
```

```{r}
# Display the UI
uiOutput("director_movies_ui")
```

### Reviews

```{r}
# 1. State management for cycling through reviews
current_review_idx = reactiveVal(1)

# Reset back to the first review when a new movie is selected
observeEvent(input$movie_table_rows_selected, {
  current_review_idx(1)
})

# Increment the index when the "Next" button is clicked
observeEvent(input$next_review_btn, {
  reviews = movie_reviews()
  if (is.data.frame(reviews) && nrow(reviews) > 0) {
    next_idx = current_review_idx() + 1
    if (next_idx > nrow(reviews)) {
      next_idx = 1
    }
    current_review_idx(next_idx)
  }
})

# 2. Fetch and process the review data
movie_reviews = reactive({
  req(input$movie_table_rows_selected)
  selected_idx = input$movie_table_rows_selected
  
  # CLEAN THE TITLE: Remove whitespace and hidden characters
  title = trimws(as.character(data$Series_Title[selected_idx]))
  tmdb_key = "46c2ebcda9588c28b102306512e4161a" 
  
  # Step A: Search for the movie ID on TMDB
  safe_title = URLencode(title, reserved = TRUE)
  
  # Splitting the "https://" prevents RStudio from auto-formatting it as a markdown link
  search_base = paste0("https://", "api.themoviedb.org/3/search/movie?query=")
  search_url = paste0(search_base, safe_title, "&api_key=", tmdb_key)
  
  search_res = tryCatch({
    jsonlite::fromJSON(search_url)
  }, error = function(e) {
    return(list(is_error = TRUE, msg = paste("HTTP/API Error on Search:", e$message)))
  })
  
  if (isTRUE(search_res$is_error)) return(search_res)
  
  if (is.null(search_res$results) || length(search_res$results) == 0 || (is.data.frame(search_res$results) && nrow(search_res$results) == 0)) {
    return(list(is_error = TRUE, msg = paste("TMDB Search successful, but 0 matches found for:", title)))
  }
  
  movie_id = search_res$results$id[1]
  
  # Step B: Get reviews for that specific movie ID
  reviews_base = paste0("https://", "api.themoviedb.org/3/movie/")
  reviews_url = paste0(reviews_base, movie_id, "/reviews?api_key=", tmdb_key)
  
  reviews_res = tryCatch({
    jsonlite::fromJSON(reviews_url)
  }, error = function(e) {
    return(list(is_error = TRUE, msg = paste("HTTP/API Error on Reviews:", e$message)))
  })
  
  if (isTRUE(reviews_res$is_error)) return(reviews_res)
  
  if (is.null(reviews_res$results) || length(reviews_res$results) == 0 || (is.data.frame(reviews_res$results) && nrow(reviews_res$results) == 0)) {
    return(data.frame()) 
  }
  
  reviews_df = reviews_res$results
  
  # Step C: Sort by author's rating (descending)
  if ("author_details" %in% names(reviews_df)) {
    ratings = as.numeric(reviews_df$author_details$rating)
    ratings[is.na(ratings)] = 0
    reviews_df$rating = ratings
    reviews_df = reviews_df[order(-reviews_df$rating), ]
  }
  
  return(reviews_df)
})

# 3. Render the specific review
output$reviews_ui = renderUI({
  reviews = movie_reviews()
  
  # Catch our custom error object and print it directly to the dashboard screen
  if (!is.data.frame(reviews) && is.list(reviews) && isTRUE(reviews$is_error)) {
    return(HTML(paste0(
      '<div style="padding: 20px; text-align: center; border: 2px dashed #d9534f; border-radius: 8px; color: #d9534f; margin-bottom: 10px;">',
      '<b style="font-size: 16px;">Diagnostic Info:</b><br><br>', reviews$msg, 
      '</div>'
    )))
  }
  
  # Normal empty state (0 reviews found on a successful movie match)
  if (is.data.frame(reviews) && nrow(reviews) == 0) {
    return(HTML('<div style="padding: 20px; text-align: center; color: #777; font-style: italic;">No reviews have been written for this movie on TMDB yet.</div>'))
  }
  
  idx = current_review_idx()
  review = reviews[idx, ]
  
  author = review$author
  content = review$content
  
  # Format the rating badge if they left one
  rating_display = ""
  if (!is.null(review$rating) && !is.na(review$rating) && review$rating > 0) {
    rating_display = paste0('<span style="background: #F4B400; color: #fff; padding: 2px 6px; border-radius: 4px; font-size: 12px; margin-left: 10px;">★ ', review$rating, '/10</span>')
  }
  
  HTML(paste0('
    <div style="padding: 15px; background: #f9f9f9; border-radius: 8px; border: 1px solid #eaeaea; margin-bottom: 10px;">
      <div style="display: flex; justify-content: space-between; align-items: center; margin-bottom: 15px;">
        <div style="font-weight: bold; font-size: 16px; color: #333;">', author, rating_display, '</div>
        <div style="font-size: 12px; color: #888;">Review ', idx, ' of ', nrow(reviews), '</div>
      </div>
      <div style="font-size: 14px; color: #555; line-height: 1.6; max-height: 200px; overflow-y: auto; padding-right: 5px;">
        ', gsub("\n", "<br>", content), '
      </div>
    </div>
  '))
})

# 4. Render the "Next" button conditionally
output$review_controls_ui = renderUI({
  reviews = movie_reviews()
  # Hide the button if there's an error or only 1/0 reviews
  if (!is.data.frame(reviews) || nrow(reviews) <= 1) {
    return(NULL) 
  }
  
  div(style = "text-align: right;",
    actionButton("next_review_btn", "Next Review ➔", 
                 style = "color: #fff; background-color: #337ab7; border-color: #2e6da4; border-radius: 4px; font-weight: 600;")
  )
})
```

```{r}
# UI rendered safely without nested raw flexbox
uiOutput("reviews_ui")
uiOutput("review_controls_ui")
```