---
title: "IMDB Movie Finder"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: PP_logotyp_ANG_RGB.png
runtime: shiny
---

<style>
.navbar-logo img {
  max-height: 80px !important; 
  width: auto !important;
}

.navbar {
  height: 80px !important;
  min-height: 80px !important; 
}
body {
  padding-top: 80px !important; 
}

.navbar-header {
  display: flex !important;
  align-items: center !important; 
  height: 80px !important;       
  width: 100% !important;
}

.navbar-logo {
  display: flex !important;
  align-items: center !important;
  padding-left: 15px !important;
  position: static !important;
}

.navbar-brand {
  flex-grow: 1 !important;
  display: flex !important;
  justify-content: center !important;
  align-items: center !important;
  margin: 0 !important;
  padding: 0 !important;
  
  font-family: 'Segoe UI', Roboto, Helvetica, Arial, sans-serif !important;
  font-size: 26px !important; 
  font-weight: 800 !important; 
  letter-spacing: 1.5px !important;
  color: #F7F7F7 !important;  
  text-shadow: 1px 1px 2px rgba(0,0,0,0.1) !important;
}
</style>

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(plotly)
library(shiny)
```

```{r, include=FALSE}
data = read.csv("IMDB top 1000.csv")
```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

